
\sectiontitle{\b{Employment} \\ \b{History}}

\employer{{\bf '12-pres., Professor, Eindhoven University of Technology, \href{http://www.sps.ele.tue.nl/}{Signal Processing Systems Group, EE dept.}}} \location{Eindhoven,
the Netherlands}
\vspace{-.8cm}
\begin{items}
  \item 1 day/week appointment; Previous engagement: Research Fellow ('04-'11)
  \item Research on \textbf{Personalization of Medical Signal Processing Systems}
  \item Teach graduate class on \href{http://www.sps.ele.tue.nl/members/b.vries/teaching/5mb20/index.html}{Adaptive Information Processing}.
  \item Inaugural lecture: "In Situ Personalization of Signal Processing Systems" (at \href{http://goo.gl/EoU0SE}{youtube}), September 2013. 
\end{items}


\employer{{\bf '99-pres., Principal Scientist, \href{http://www.gnresound.dk/}{GN ReSound} (Philips Hearing Technologies until 2001) }} \location{Eindhoven, the
Netherlands}
\vspace{-.8cm}
\begin{items}
  \item Other engagements include: DSP Functional Leader ('11-pres.), Head DSP Research ('08-'11), Manager External Research ('01-'08), Technology Leader ('99-'01, Philips)
  \item Research PI on low-power signal processing technology for the next
generation of digital hearing aids.
  \item Leadership/management tasks include(d) all aspects
of team and project management (teams of about 10 engineers); (responsible for) the corporate DSP research track, including the roadmap, budget and management; initiating and managing key studies at academic institutions and contract research organizations.
\end{items}




\employer{{\bf '93-'99, Member Technical Staff,  \href{http://www.sarnoff.com/}{Sarnoff
Corporation}}} \location{Princeton, NJ} 
\vspace{-.8cm}
\begin{items}
\item Research in advanced signal processing algorithms, initiating new technical and commercial thrusts, technical proposal writing and project management.
\item Principal investigator of funded projects on keyword spotting, digital hearing aids signal processing, speech enhancement and noise-robust speech recognition (co-PI). 
\item Co-initiated and developed signal processing in financial markets program at Sarnoff.
\item Member medical image processing research team. Funded projects include blind signal processing for breast mammography and perceptually optimized image coding.
\end{items}

\employer{{\bf '92-'93, Postdoctoral Fellow, David Sarnoff
Research Center}} \location{Princeton, NJ} 
\vspace{-.8cm}
\begin{items}
\item Developed neural
network based speech recognition method (50\% error reduction
relative to competing methods).
\end{items}

\employer{{\bf '87-'91, Research/Teaching Assistant,  University
of Florida}} \location{Gainesville, FL} 
\vspace{-.8cm}
\begin{items}
\item Taught and assisted in graduate classes in digital signal processing, control theory and computer architecture. 
\end{items}