
%\newpage
\sectiontitle{\b{Publications}}

\employer{{\bf Impact Factor}}
\begin{itemize}
\item 10 journal articles, 13 patents, $>$50 conference contributions with  citation numbers (high to low) $\r{146,108,69,33,33,31,30,29,21,16,14,12},11,11,10,7,7,\ldots \Rightarrow$ Hirsch-index $= 12$, Google Scholar, Feb-2011.
\item ($>$60 unpublished technical reports (company confidential))
\end{itemize}


\employer{{\bf Journal Articles and Book Chapters}}

%\renewcommand{\refname}{\vspace{-1.5cm}}
\begin{etaremune}

\item Rik Vullings et al.\, An Adaptive Kalman Filter for ECG Signal Enhancement, \emph{IEEE Transactions on Biomedical Engineering}, vol.58, no.4, April 2011.

%\item \gray{Bert de Vries et al., Evidence-based design of hearing aid algorithms, submitted to \emph{J. acoustic soc. of America}, Jan.\ 2008.}

\item A.\ Ypma et al., \href{http://www.hindawi.com/GetArticle.aspx?doi=10.1155/2008/183456}{On-line Personalization of Hearing Instruments}, \emph{EURASIP Journal on Audio, Speech, and Music Processing}, September 2008.

\item  Tjeerd Dijkstra et al., \href{http://www.hearingreview.com/issues/articles/2007-10_05.asp}{The Learning Hearing Aid: Common-Sense Reasoning in Hearing Aid Circuits}, The Hearing Review, issue October 2007. (cited by 5, GS1102 (=Google Scholar, 2011-02))

%\item \gray{Thomas Beierholm et al., Non-Stationary Noise Reduction by Particle Filtering in a Cascade Formant Synthesizer Model, submitted to \emph{IEEE Trans. on Audio, Speech and Language Processing}, June 2007}

\item David Zhao et al., On-line Noise Estimation Using Stochastic-Gain HMM for Speech Enhancement, \emph{IEEE Transactions on Audio, Speech and Language Processing}, vol.16, no.4, May 2008. (cited by 2, GS0808)

\item Jose Principe et al., Locally Recurrent Networks: The Gamma
Operator, Properties and Extensions, invited book chapter in {\em
Neural Networks and Pattern Recognition}, Omidvar and Dayhoff
(eds.), Academic Press, 1997. (cited by 1, GS0907)

\item Bert de Vries, Short term memory structures for dynamic neural networks, book chapter in:
{\em Artificial Neural Networks for Speech and Vision}, Richard Mammone (ed.), Chapman \& Hall Ltd.,
1994. (cited by 3, GS0810)

\item Bert de Vries and Jose Principe, The gamma model--A new neural
network for temporal processing, {\em Neural Networks} vol. 5(4),
pp. 565-576, 1992. \r{(cited by 146, GS1102)}

\item Jose Principe and Bert de Vries, The gamma filter--A new class of adaptive IIR filters
with restricted feedback,  {\em IEEE transactions on signal
processing}  vol. 41(2), pp. 649-656, 1992. \r{(cited by 108, GS1102)}

\item Bert de Vries, \href{http://ufdc.ufl.edu/UF00082173/00001}{Temporal processing with neural networks-the development of the Gamma model},
{\em Ph.D. dissertation}, University of Florida, 1991. \r{(cited by 12, GS1102)}

\item Joachim Gravenstein et
al., Sampling intervals for clinical monitoring of variables during
anesthesia,  {\em Journal of clinical monitoring} vol 5(1), 1989. \r{(cited by 30, GS1102)}

\item Jan J. van der Aa, Bert de Vries and Joachim
Gravenstein, Toward more sophisticated monitoring alarms,  {\em
Journal of clinical monitoring} 4 (2), 1986.

\end{etaremune}
 

%\newpage
\employer{{\bf Patents}}

\begin{etaremune}

\item Andrew Dittberner et al., A Location Learning Hearing Aid, filed by GN ReSound with Danish Patent and Trademark Office, December 2013

\item Bert de Vries and Mojtaba Farmani, A Hearing Aid with Probabilistic Hearing Loss Compensation, filed by GN ReSound with US Patent and Trademark Office, App. number 14077031, Nov. 2013 

\item Bert de Vries et al., Efficient evaluation of hearing ability, submitted by GNR Ref.: P1669 EP, Albihns Ref.: P13304 US / P13303, April 2009.

\item Alexander Ypma et al., Asymmetric synchronization of hearing aid algorithms, submitted by GN ReSound, patent no. 09174982.0-2225, filed 4-Nov-2009.

\item Alexander Ypma et al., Learning control of hearing aid parameter settings, submitted by GN ReSound, filed 16-Mar-2007.

\item Bert de Vries and Alexander Ypma, Optimization of Hearing Aid Parameters, filed by GN ReSound, patent no. WO/2007/042043, 10/13/06.

\item Bert de Vries, Bastiaan Kleijn, Alexander Ypma and David Zhao, Method and Apparatus for Improved Estimation of Non-stationary Noise for Speech Enhancement, filed by GN ReSound, patent no. 06119399.1-224, 08/23/06

\item Bert de Vries and Rob de Vries, Fitting methodology and hearing prosthesis based on signal-to-noise ratio loss data, USA patent registered for
GN ReSound, no. 20040047474, 03/11/2004.

\item L. Parra and B. de Vries, Method and apparatus for adaptive speech detection by applying a probabilistic description to the classification and tracking of signal components, patent registered for Sarnoff Corporation, LG Electronics, Inc., no. 6691087, 10-Feb. 2004. (cited by 3, GS1102)

\item Bert de Vries, Noise Spectrum Tracking for Speech Enhancement,
patent registered for Sarnoff Corporation, no. US6289309,
9/11/2001. \r{(cited by 29, GS1102)}

\item  J. Lubin et al., Method and apparatus for training a neural network to learn and use fidelity metric as a control mechanism, patent registered for
Sarnoff Corporation, no. US6075884, 6/13/2000. \r{(cited by 14, GS1102)}

\item Bert de Vries, Method and apparatus for filtering signals using a gamma delay line based estimation of power spectrum, patent
registered for Sarnoff Corporation, no. US6073152, 6/6/2000. (cited by 1, GS1102)

\item M. Brill, J. Lubin, B. de Vries, O. Finard, Method and apparatus for assessing the visibility of differences between two image sequences, patent registered for Sarnoff Corporation, no.
US5974159, 10/26/1999. \r{(cited by 33, GS1102)}

\item Bert de Vries, Method and system for training a neural network with adaptive
weight updating and adaptive pruning in principal components space,
patent registered for David Sarnoff Research
Center, no. 5,812,992, 9/22/98. \r{(cited by 21, GS1102)}

\item Bert de Vries and Jose Principe, An adaptive filter based on a recursive delay line,  patent registered
for University of Florida, no. 5,301,135, April 1994. (cited by 5, GS1102)

\end{etaremune}

% \employer{{\bf Sarnoff Technical Reports}}

% \begin{etaremune}

% \item Bert de Vries, Uday Jain, Lucas Parra, Low-complexity spectrum
% based speech enhancement, \emph{Sarnoff Technical Report}, March
% 1998.

% \item Bert de Vries, Finding dependencies in foreign exchange rate data
% by the delta test, \emph{Sarnoff Technical Report}, December 1995.

% \item Bert de Vries, Adaptive prediction with error bars and an
% application to foreign currency trading, \emph{Sarnoff Technical
% Report}, July 1995.

% \item Bert de Vries, Adaptive eigenpruning for non-stationary time
% series modeling with applications to foreign exchange rate
% forecasting, \emph{Sarnoff Technical Report}, October 1994.

% \end{etaremune}

\employer{{\bf Conferences and Workshops}}
\begin{etaremune}

\item Bert de Vries and Andrew Dittberner, Is Hearing Aid Signal Processing Ready for Machine Learning? \emph{Int'l Symposium on Auditory and Audiological Research}, Nyborg, DK, Aug. 2013

\item Ungureanu C. et al., A Bayesian Network for Detection of Seizures, \emph{1st Jan Beneken Conference on Modeling and Simulation of Human Physiology}, Eindhoven, NL, 2013

\item Petkov P. et al., Discrete Choice Models for Non-Intrusive Quality Assessment, \emph{Interspeech 2011}, Florence, Italy, 2011

\item Rob de Vries et al., A software suite for automatic beamforming calibration, \emph{Int'l Hearing Aid Research Conference}, Lake Tahoe, CA, August 2010

\item S.I. Mossavat et al., A Bayesian hierarchical mixture of experts approach to estimate speech quality, \emph{QoMEX 2010},  Trondheim, Norway, June 2010

\item Jos Leenen and Bert de Vries, Current DSP and Machine Learning Trends in the Hearing Aids Industry,  \emph{IEEE Benelux Signal Processing Symposium: Signal Processing for Digital Hearing Aids}, Delft, NL, April 2010

\item Xueru Zhang et al., Bayesian periodogram smoothing for speech enhancement, \emph{European Symposium on Artificial Neural Networks (ESANN-09)}, Bruges, April 2009

\item Adriana Birlutiu et al., Towards hearing aid personalization: preference elicitation from audiological data, \emph{Scientific ICT-Research Event Netherlands (SIREN)}, Amsterdam, Sep. 2008

\item Tjeerd Dijkstra et al., HearClip: an Application of Bayesian Machine Learning to Personalization of Hearing Aids, Presentation at \emph{Dutch Society for Audiology Meeting}, Sep. 2008

\item Bert de Vries, Fast Model-Based Fitting through Active Data Selection, \emph{Int'l Hearing Aid Research Conference}, Lake Tahoe, CA, August 2008

\item Rolph Houben et al., Construction of a virtual subject response database to reduce subject testing, \emph{Int'l Hearing Aid Research Conference}, Lake Tahoe, CA, August 2008

\item Bert de Vries et al., The Complexity of Hearing Aid Fitting, presented at \emph{International Symposium on Auditory and Audiological Research 2007}, Helsingor, Denmark, August 2007

\item Jos Leenen et al., Learning Volume Control for Hearing Aids, presented at \emph{International Symposium on Auditory and Audiological Research 2007}, Helsingor, Denmark, August 2007

\item Alexander Ypma et al., Bayesian Feature Selection for Hearing Aid Personalization,  \emph{MLSP-07}, Thessaloniki, Greece, 2007. (cited by 2, GS1102)

\item Adriana Birlutiu et al., Personalization of Hearing Aids through Bayesian Preference Elicitation, \emph{NIPS workshop on User Adaptive Systems}, Whistler, BC, Canada, December 2006

\item Bert de Vries et al., Bayesian Machine Learning for Personalization of Hearing Aid Algorithms, \emph{Int'l Hearing Aid Research Conference}, Lake Tahoe, CA, August 2006

\item Alexander Ypma, Bert de Vries and Job Geurts, Robust Volume Control Personalization from On-line Preference Feedback, \emph{IEEE Int. Workshop on
Machine Learning for Signal Processing}, Maynooth, Ireland, 2006. (cited by 4, GS1102)

\item Bert de Vries, Tom M. Heskes and Tjeerd M. H. Dijkstra, Bayesian Incremental Utility Elicitation with Application to Hearing Aids Personalization, \emph{Valencia/ISBA 8th World Meeting on Bayesian Statistics}, Benidorm, Spain, June 2006

\item Tjeerd M. H. Dijkstra et al., A Bayesian decision-theoretic framework for psychophysics, \emph{Valencia/ISBA 8th World Meeting on Bayesian Statistics}, Benidorm, Spain, June 2006

\item Alexander Ypma, Bert de Vries and Job Geurts, A learning volume control that is robust to user inconsistency,  \emph{The second annual
IEEE BENELUX/DSP Valley Signal Processing Symposium}, Antwerp, March 2006

\item Paul Aelen et al., Electrohysterographic Estimation of the Intra-Uterine Pressure, \emph{The second annual
IEEE BENELUX/DSP Valley Signal Processing Symposium}, Antwerp, March 2006

\item Tom Heskes and Bert de Vries, Incremental Utility Elicitation for Adaptive
Personalization, \emph{The 17th Belgian-Dutch Conference on Artificial Intelligence}, Brussels, Belgium, October 2005. (cited by 6, GS1102)

\item Bert de Vries and Rob de Vries, An Integrated Approach to Hearing Aid Algorithm Design, \emph{Int'l Hearing Aid Research Conference},
Lake Tahoe, CA, August 2004

\item Harald Pobloth et al., Speech Coding for Wireless Communication
in the Hearing Aid Environment, \emph{Int'l Hearing Aid Research Conference},
Lake Tahoe, CA, August 2004

\item Bert de Vries and Rob de Vries,An Integrated Approach to Hearing
Aid Algorithm Design for Enhancement of Audibilit y,
Intelligibility and Comfort, \emph{IEEE Benelux Signal Processing
Symposium}, Hilvarenbeek, Netherlands, April 2004. (cited by 4, GS1102)

\item Rob de Vries and Bert de Vries, Toward SNR-Loss Restoration in Digital Hearing Aids, {\em ICASSP 2002}, Orlando, FL, May 2002. (cited by 4, GS0801)

\item Bert de Vries, Jos Leenen, A Low Power Digital AGC Circuit for
Dynamic Range Control of an A/D Converter, {\em International
Hearing Aids Research (IHCON) Conference 2000}, Lake Tahoe (CA),
August 2000

%Bert de Vries, Improved Noise Spectrum Tracking for Speech
%Enhancement, submitted to {\em ICASSP'99}
%\item

\item Lucas Parra, Clay Spence and Bert de Vries, Convolutive Blind Source
Separation based on Multiple Decorrelation, {\em IEEE workshop on Neural
Networks for Signal Processing VIII}, pp.23-32, Cambridge, UK, 1998. \r{(cited by 69, GS1102)}

\item Bert de Vries, Blind Signal Processing for Hearing Aids, {\em NIH Hearing Aids Improvement Conference}, Bethesda, MA, May 1997

\item Bert de Vries, Adaptive Gamma Filters for Miniature Hearing Aids, {\em NIH Hearing Aids Improvement Conference},
Bethesda, MA, May 1997

\item Bert de Vries, Adaptive rank filtering based on error minimization,
{\em ICASSP-97}, Munich, April 1997

\item Lucas Parra, Clay Spence, Bert De Vries, Convolutive Source Separation
and Signal Modeling with Maximum Likelihood, {\em International
Symposium on Intelligent Systems} (ISIS'97), 1997, Regio Calabria,
Italy. \r{(cited by 10, GS1101)}

\item Q. Lin et al., Robust distant-talking speech recognition,  {\em
ICASSP-96}, Atlanta,GA, May 1996. \r{(cited by 16, GS1102)}

\item Bert de Vries et al., Neural network speech enhancement for noise robust speech recognition,
{\em International Workshop on Applications of Neural Networks to Telecommunications}, Sweden, May
1995. (cited by 2, GS1102)

\item Lin et al., Experiments on distant-talking speech recognition, {\em ARPA Workshop on Spoken
Language Technology}, Austin, TX, January 1995.\r{(cited by11, GS1102)}

\item Qiguang Lin et al., System of microphone arrays and neural networks for robust speech recognition in multimedia
environments, Proceedings {\em International Conference on Spoken Language
Processing}, Yokohama, Japan, September 1994. (cited by 8, GS1102)

\item Bert de Vries, Gradient-based adaptation of network structure, {\em International Conference on
Artificial Neural Networks 94}, Sorrento, Italy, May 94.

\item Che et al., Microphone Arrays and Neural Networks for Robust Speech
Recognition, {\em ARPA
Workshop on Human Language Technology}, Princeton, NJ, March 1994.\r{(cited by 33, GS1102)}

\item Bert de Vries et al., An application of Gamma delay lines to "BDG" phoneme classification,
{\em Government Microcircuit Applications Conference proceedings}, New
Orleans, LA, November 1993.

\item Bert de Vries, Time-varying neural networks for large tasks, {\em International Conference on Artificial
Neural Networks proceedings}, Amsterdam, the Netherlands, September
13-16, 1993.

\item  J.C. Principe et al., Backpropagation through time with fixed memory size requirements, \emph{Proceedings of Workshop on Neural Networks for Signal Processing}, Linthicum Heights, MD, USA, Sep. 1993. (cited by 1, GS1102)

\item Bert de Vries et al.,Learning with target trajectory constraints for sequence classification tasks,
{\em ICASSP-93}, Minneapolis, MN, April 1993.

\item Bert de Vries et al.,Short Term Memory Structures for Dynamic Neural
Networks,  {\em Asilomar-92}
Conference proceedings, Pacific Grove, CA, 1992. (cited by 3, GS1102)

\item T. Oliveira a Silva et al., Generalized feedforward filters with
complex poles, {\em Proceedings of the
1992 IEEE workshop on Neural Networks for Signal Processing},
Copenhagen, Denmark, 1992.

\item Jyh-Ming Kuo, Jose Principe and Bert de
Vries, Prediction of chaotic time series using recurrent networks,
{\em Proc. of the 1992 IEEE workshop on Neural Networks for Signal
Processing}, 1992. \r{(cited by 7, GS1102)}

\item Jose Principe, Bert de Vries and
Pedro G. de Oliveira, Generalized feedforward structures: a new class
of adaptive filters, {\em ICASSP-92}, San Francisco, vol. IV,
pp. 245-248, 1992. \r{(cited by 7, GS0801)}

\item T. Oliveira e Silva, P. Guedes de Oliveira, J. C. Principe and B.
de Vries, A Complex Pole Extension to the Gamma Filter, {\em The
INESC Journal of Research and Development}, vol. 3, no. 1, pp.
35-41, Jan./Jun. 1992.

\item Bert de Vries et al., Adaline with adaptive recursive memory, {\em Proceedings IEEE workshop on signal
processing}, Princeton, NJ, 1991. \r{(cited by 11, GS1102)}

\item Principe et al., Modeling applications with the focused gamma
net,  {\em NIPS-4 proceedings},
Denver, CO, 1992. \r{(cited by 6, GS0810)}

\item Bert de Vries et al., Some practical issues concerning the gamma
neural net, {\em Proceedings IJCNN-91},
Seattle, WA, 1991.

\item Bert de Vries and Jose Principe, A theory for neural nets with time
delays, {\em NIPS-3 Proceedings},
Denver, 1991. \r{(cited by 31, GS1102)}

\item Bert de Vries et al., Neural net models for temporal processing, {\em Proceedings nineth southern biom. eng. conference}, Miami, FL, 1991.

\item Bert de Vries et al., A new neural net model for temporal processing,
{\em 12th ann. int. conf. IEEE on
the eng. in medicine and biology society}, Philadelphia, PA, 1990.

\item Bert de Vries et al., Artificial neural networks as a computational paradigm for detection of anaesthetic complications,
{\em Computers in Anesthesia 10}, New Orleans, LA, 1989.

\item Bert de Vries et al., Distribution of anesthesia related occurrences during surgical operations,
{\em Anesthesiology review} 14 (6), 1987.

\end{etaremune}
