\sectiontitle{\b{TU/e Univ.} \\ \b{Activities}}
\employer{{\bf Teaching}}
\begin{items}
\item \href{http://www.sps.ele.tue.nl/members/b.vries/teaching/5mb20/home.html}{\textbf{Adaptive Information Processing}}. Together with \href{http://www.sps.ele.tue.nl/members/T.J.Tjalkens}{Tjalling Tjalkens}, since spring 2005 I teach a core graduate class on the fundamentals of machine learning.
\item \href{http://www.sps.ele.tue.nl/members/b.vries/teaching/mlrc04/home.html}{\textbf{Machine Learning}}. I organized a machine learning reading club for TU/e graduate students and GN ReSound staff. Fall 2004.
\end{items}

\employer{{\bf Research}}

My current research focuses on applications of Bayesian machine learning to personalization of hearing aid algorithms. In July 2006, together with  \href{http://www.cs.ru.nl/staff/Tom.Heskes}{Tom Heskes} and \href{http://www.ac-amc.nl/medewerkers/dreschler.html}{Wouter Dreschler}, we received a $650$K euro grant from \href{http://www.stw.nl}{STW} to pursue further research on \emph{Personalization of Hearing Aids through Bayesian Preference Elicitation}.

\employer{{\bf Recent Student Supervision}}
\begin{items}
\item Brian Hutama Susilo, M.Sc. practical training project, \emph{Automated Tuning Algorithm for Low-latency PC-based Audio Processing}, Dec. 2013
\item Zijian Xu, M.Sc. thesis project, \emph{Fast Design of Audio Processing Algorithms by Interactive Parameter Exploration}, August 2013
\item Timur Bagautdinov, M.Sc. thesis project, \emph{A Machine Learning Framework for Signal Processing}, August 2013 
\item Marno van der Maas, B.Sc. research project, \emph{Browser-based Remote Control of Hearing Aids}, June 2013
\item Maarten Thomassen, M.Sc. practical training project, \emph{Spectral Audio Monitoring}, July 2012
\item Joris Kraak, M.Sc.-thesis, \emph{Computer-Aided Algorithm Design for Audio Processing}, April 2012
\item Joris Kraak, M.Sc. practical training project, \emph{Optimization of a Spectral 
Noise Tracking Algorithm}, Dec. 2010
\item Jianfeng Li, M.Sc.-thesis, \emph{Acoustic scene-adaptive speech enhancement}, Aug. 2010
\item Jianfeng Li, M.Sc.-project, \emph{Spatial defect clustering on semiconductor wafers using image processing techniques}, Aug.-2009
\item Xueru Zhang, P.D.Eng.-thesis: \emph{Bayesian periodogram smoothing for speech enhancement}, Sep. 2008
\item Rene Besseling, M.Sc.-project, \emph{Gaussian processes in Bekesy audiometry}, June 2008
\item Serkan Ozer, M.Sc.-thesis: \emph{Bayesian linear regression for user-adaptive hearing aids}, Aug. 2007
\item Ronnie van Loon, M.Sc.-thesis: \emph{a Probabilistic Approach to Sound Classification}, June 2007.
\item Anton Vakrushev, P.D.Eng.-thesis: \emph{Interactive machine learning for Personalization of hearing aid algorithms}, Sep. 2006
\item Jorik Caljouw, M.Sc. practical training on \emph{PDA-based Interfacing to a real-time audio platform}, Dec. 2005.
\item Paul Aelen, M.Sc. project, \emph{Determination of the Intra Uterine Pressure with electrodes on the abdomen}, Dec. 2005.
\item Job Geurts, M.Sc. practical training on \emph{A PC-based real-time simulation platform for evaluating hearing aid algorithms}, Jun. 2005.
\end{items}


\employer{{\bf Care and Cure theme}}

I actively participated in the development of the Care and Cure theme roadmap for the EE department (2008).  